Named Entity Recognition as Structured Prediction

### 2012-11-11 doc/report/paper.tex
corrections

Precision is the percentage of Named Entities found by the system that are correct. Recall is the percentage of Named Entities present in the corpus that were 
found by the system. A Named Entity is only deemed correct if it is an exact match for the corresponding data file. The general formula for the \emph{F-Score} 
is shown below. Since we consider \emph{precision} and \emph{recall} as equally important, we use the $F_{1}$ score, which is the harmonic mean of precision and recall.
\begin{align*}
  F_{\beta} &=  (1+\beta^2)*\frac{precision *recall}{\beta^2* precision + recall}\\
  F_1       &= 2*\frac{precision *recall}{precision + recall}\\
\end{align*}

>>>>

Precision is the percentage of Named Entities found by the system that are correct. Recall is the percentage of Named Entities present in the corpus that were 
found by the system. A Named Entity is only deemed correct if it is an exact match for the corresponding data file. The general formula for the \emph{F-score} 
is shown below. Since we consider precision and recall as equally important, we use the $F_{1}$-score, which is the harmonic mean of precision and recall.
\begin{align*}
  F_{\beta} &=  (1+\beta^2)*\frac{precision *recall}{\beta^2* precision + recall}\\
  F_1       &= 2*\frac{precision *recall}{precision + recall}\\
\end{align*}
